First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2016-09-07 analysis-note-v2/data_analysis.tex

The fastmc is applied to the Monte-Carlo generated $^{4}He$ for the channels 
$e^{4}He\gamma$ and $e^{4}He\pi^{0}$. We do not specifically apply energy loss 
and multiple scattering in our fastmc, but we do apply resolution effects based 
on experimental data that include both effects. The plots in figure 
\ref{fig:comp_He} show the comparison between data and simulation in terms of 
theta, $phi$ and momentum of the $^{4}$He DVCS nuclei, that will presented in 
details in the following chapter. The other particles, ($e^{-}$, $p$, 
$\gamma$), are fed to GSIM through the previously mentioned 
simulation-reconstruction chain procedures.

>>>>

The fastmc is applied to the Monte-Carlo generated $^{4}He$ for the channels 
$e^{4}He\gamma$ and $e^{4}He\pi^{0}$. We do not specifically apply energy loss 
and multiple scattering in our fastmc, but we do apply resolution effects based 
on experimental data that include both effects. The plots in figure 
\ref{fig:comp_He} show the comparison between data and simulation in terms of 
$\theta$, $\phi$ and momentum of the $^{4}$He DVCS nuclei, that will presented 
in details in the following chapter. The other particles, ($e^{-}$, $p$, 
$\gamma$), are fed to GSIM through the previously mentioned 
simulation-reconstruction chain procedures.

### 2016-09-07 eg6-letters/coherent/HeliumCohDVCS.tex

\begin{abstract}
We report the first exclusive measurement of deeply virtual Compton scatterring 
(DVCS) off a nuclei with the CLAS detector at the Jefferson laboratory. The 
observed beam spin asymmetries are significantly larger than for proton, 
confirming expectations from calculations using the plane wave impulse 
approximation. We present an 
extraction of the single generalized parton distribution (GPD) of the spin-0 
helium-4 nuclei in a completely model independent way. This result demonstrate the 
strength of the method and opens a new and unique access into the partonic structure 
of nuclei.
\end{abstract}

>>>>

\begin{abstract}
We report the first exclusive measurement of deeply virtual Compton scattering 
(DVCS) off a nuclei with the CLAS detector at the Jefferson laboratory. The 
observed beam spin asymmetries are significantly larger than for proton, 
confirming expectations from calculations using the plane wave impulse 
approximation. We present an 
extraction of the single generalized parton distribution (GPD) of the spin-0 
helium-4 nuclei in a completely model independent way. This result demonstrate the 
strength of the method and opens a new and unique access into the partonic structure 
of nuclei.
\end{abstract}
